---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pushoverr

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/briandconnelly/pushoverr/branch/master/graph/badge.svg)](https://app.codecov.io/gh/briandconnelly/pushoverr?branch=master)
[![R-CMD-check](https://github.com/briandconnelly/pushoverr/workflows/R-CMD-check/badge.svg)](https://github.com/briandconnelly/pushoverr/actions)
[![CRAN status](https://www.r-pkg.org/badges/version/pushoverr)](https://CRAN.R-project.org/package=pushoverr)
<!-- badges: end -->

pushoverr allows you to send push notifications from R to mobile devices, web browsers, or even your watch using [Pushover](https://pushover.net/).
These notifications can display job status, results, scraped web data, or any other text or numeric data.
Got some R code that takes a while to complete?
Enough time to take a little walk or go get a coffee, but maybe not long enough to go home for the day?
Now you'll be able to easily let yourself or your group know when it's done.


## Prerequisites

You'll need an account with [Pushover](https://pushover.net/).
Once you have that, log in and [register an application](https://pushover.net/apps/build).
You should now have two codes---a **user key** and an **API token/key**.
These are what identify you and your app(s) to Pushover.
You'll pass these along to pushoverr whenever you send a message.
You'll also need the Pushover app for [iOS](https://pushover.net/clients/ios), [Android](https://pushover.net/clients/android), or your [desktop](https://pushover.net/clients/desktop).


## Installation

Installing pushoverr is as easy as running:

```{r eval=FALSE}
install.packages("pushoverr")
```

Alternately, you can install the development version of pushoverr from [GitHub](https://github.com/) with:

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("briandconnelly/pushoverr")
```


## Features Not Supported

pushoverr currently does not support [subscriptions](https://pushover.net/api/subscriptions/), [licensing](https://pushover.net/api/licensing/) (I don't use Pushover in this context, so I can't test these features), or the [open client API](https://pushover.net/api/client/).
If you'd like to see these features supported, please submit an [issue](https://github.com/briandconnelly/pushoverr/issues) or a pull request.


## Related Links
* [Pushover](https://pushover.net/)
    * [Support](https://support.pushover.net/)
    * [API](https://pushover.net/api/)
    * [Terms of Service](https://pushover.net/terms/)
* [R Phone Home: Notifications with pushoverr](http://bconnelly.net/2016/11/R-phone-home/), blog post about using pushoverr
* [NotifyR](https://cran.r-project.org/package=notifyR), an alternate Pushover tool for R (no longer maintained?)
* [RPushbullet](https://eddelbuettel.github.io/rpushbullet/), an R interface for [Pushbullet](https://www.pushbullet.com/), a similar push notification service.


## Code of Conduct

Please note that the pushoverr project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.


## Disclaimer

This package and its author are not affiliated with Pushover, LLC.
